### 2023-04-03 reachable-resilience.tex
added results from [9] on safe clos par le bas bad clos par le haut mais je trouve c'est bizare

>>>>

\begin{definition}{marked WSTS} 
A {\em marked} WSTS is a tuple $(S, \leq, \to, INIT)$
where $(S, \leq, \to)$ is a WSTS and $INIT \subseteq S$. 
If $INIT$ is finite, we call it {\em fin-marked}.
\end{definition}

\begin{definition}
A marked WSTS is
\begin{itemize}
\item lossy if $\downarrow \post^* (INIT) = \post^* (INIT)$,
\item $\bot$-bounded (bottom-bounded) if there is a natural number 
$\ell \geq 0$ s.t. $s_B \in \post^{\leq \ell} (s) $ for every $ s \in S$ and every element 
$s_B$ of a basis of $S$ with $s \geq s_B$.
\end{itemize}
\end{definition}

\mathieu{}
